---
title: "Assignment 4"
author: "Minsub Lee"
date: "2022-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.	Discuss the business problem/goal (5 points)

Dataset is to analyze Uber pickups in New York City

## 2.	identify where the dataset was retrieved from (2 points)

Dataset is rretrieved from Uber, but this dataset specifically was from stored dataset in Googledrive.

## Installing all packages

```{r include = TRUE, echo=TRUE}
library(ggplot2)
library(ggthemes)
library(lubridate)
library(dplyr)
library(tidyr)
library(DT)
library(scales)
colors = c("#CC1011", "#665555", "#05a399", "#cfcaca", "#f5e840", "#0683c9", "#e075b0")
```


## 3.	identify the code that imported and saved your dataset in R (3 points)

```{r include = TRUE, echo=TRUE}
apr_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-apr14.csv")
may_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-may14.csv")
jun_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-jun14.csv")
jul_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-jul14.csv")
aug_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-aug14.csv")
sep_data <- read.csv("C:/Users/14802/Desktop/Minsub/Master/ANA515/WK8/dataset/uber-raw-data-sep14.csv")

data_2014 <- rbind(apr_data,may_data, jun_data, jul_data, aug_data, sep_data)

data_2014$Date.Time <- as.POSIXct(data_2014$Date.Time, format = "%m/%d/%Y %H:%M:%S")

data_2014$Time <- format(as.POSIXct(data_2014$Date.Time, format = "%m/%d/%Y %H:%M:%S"), format="%H:%M:%S")

data_2014$Date.Time <- ymd_hms(data_2014$Date.Time)

data_2014$day <- factor(day(data_2014$Date.Time))
data_2014$month <- factor(month(data_2014$Date.Time, label = TRUE))
data_2014$year <- factor(year(data_2014$Date.Time))
data_2014$dayofweek <- factor(wday(data_2014$Date.Time, label = TRUE))
data_2014$hour <- factor(hour(hms(data_2014$Time)))
data_2014$minute <- factor(minute(hms(data_2014$Time)))
data_2014$second <- factor(second(hms(data_2014$Time)))
```

## 4.	describe your data set (using the common attributes such as #rows, #columns, variable names, types, means, SD, min/max, NAs, etc...) (10 points)
There are `r nrow(data_2014)` row of data, `r ncol(data_2014)` of columns. \
Column Names : `r colnames(data_2014)`\
Summary :\ 
`r summary(data_2014)`\
\
## 5.	discuss any data preparation, missing values and errors (10 points) (if the dataset was clean and there is no prep in the code, include a comment that explains what likely data preparation was done. What are the common issues with raw data?)
Data is clean for this dataset. For this data, data preparation for missing and abnormal data must be cleaned such as trip hours recorded wrongfully (location data exists but without time keeping). 

## 6.	discuss the modeling (10 points)
This project did not specifically mention about any regression or modeling. However, I strongly think that we could have regression modeling to configure typical drive hour by location and month. 

## 7.	produce and discuss the output (10 points)
This project has many data visualization output. Within project itself, we could tell the hours of Uber driven in New York by month. September was the peak months for the Uber driver based on the dataset, while the April was the slowest month among data. \
However, I also learned the techniques we could use for the future dataset analyzation. Since this project also recorded the location, we were able to provide heat map of the NYC with hours driven. I believe these type of data visualization can be very useful when it comes to location base dataset, such as crime rate by region. 

## 8.	provide explanation with any visuals (10 points) (if there are no visualizations in your code, discuss a visualization that would be useful to this project)
There are many data visualization in this project from this point. I Each data visualization has header that explains the analyzation. I would like to talk about the best data visualization among shown in this project. I personally think that the bar chart with title 'Trips by Hour and Month' is the best data visualization to explain this dataset. The reason is that it does clean visual comparison by months and people can easily tell which month had longest hours of drive from the chart

## Plotting the trips by the hours in a day

```{r include = TRUE, echo=TRUE}
hour_data <- data_2014 %>%
           group_by(hour) %>%
               dplyr::summarize(Total = n()) 
datatable(hour_data)

ggplot(hour_data, aes(hour, Total)) + 
        geom_bar( stat = "identity", fill = "steelblue", color = "red") +
           ggtitle("Trips Every Hour") +
            theme(legend.position = "none") +
            scale_y_continuous(labels = comma)

month_hour <- data_2014 %>%
          group_by(month, hour) %>%
             dplyr::summarize(Total = n())

ggplot(month_hour, aes(hour, Total, fill = month)) + 
       geom_bar( stat = "identity") +
          ggtitle("Trips by Hour and Month") +
           scale_y_continuous(labels = comma)
```

## Plotting data by trips during every day of the month


```{r include = TRUE, echo=TRUE}
day_group <- data_2014 %>%
          group_by(day) %>%
             dplyr::summarize(Total = n()) 
datatable(day_group)

ggplot(day_group, aes(day, Total)) + 
        geom_bar( stat = "identity", fill = "steelblue") +
           ggtitle("Trips Every Day") +
            theme(legend.position = "none") +
            scale_y_continuous(labels = comma)

day_month_group <- data_2014 %>%
         group_by(month, day) %>%
             dplyr::summarize(Total = n())

ggplot(day_month_group, aes(day, Total, fill = month)) + 
        geom_bar( stat = "identity") +
           ggtitle("Trips by Day and Month") +
            scale_y_continuous(labels = comma) +
            scale_fill_manual(values = colors)
```


## Number of Trips taking place during months in a year


```{r include = TRUE, echo=TRUE}
month_group <- data_2014 %>%
          group_by(month) %>%
             dplyr::summarize(Total = n()) 
datatable(month_group)

ggplot(month_group, aes(month, Total, fill = month)) + 
        geom_bar( stat = "identity") +
           ggtitle("Trips by Month") +
            theme(legend.position = "none") +
            scale_y_continuous(labels = comma) +
            scale_fill_manual(values = colors)

month_weekday <- data_2014 %>%
         group_by(month, dayofweek) %>%
             dplyr::summarize(Total = n())

ggplot(month_weekday, aes(month, Total, fill = dayofweek)) + 
       geom_bar( stat = "identity", position = "dodge") +
          ggtitle("Trips by Day and Month") +
           scale_y_continuous(labels = comma) +
           scale_fill_manual(values = colors)
```



## Finding out the number of Trips by bases


```{r include = TRUE, echo=TRUE}
ggplot(data_2014, aes(Base)) + 
 geom_bar(fill = "darkred") +
 scale_y_continuous(labels = comma) +
 ggtitle("Trips by Bases")

ggplot(data_2014, aes(Base, fill = month)) + 
 geom_bar(position = "dodge") +
 scale_y_continuous(labels = comma) +
 ggtitle("Trips by Bases and Month") +
 scale_fill_manual(values = colors)

ggplot(data_2014, aes(Base, fill = dayofweek)) + 
 geom_bar(position = "dodge") +
 scale_y_continuous(labels = comma) +
 ggtitle("Trips by Bases and DayofWeek") +
 scale_fill_manual(values = colors)
```


## Creating a Heatmap visualization of day, hour and month


```{r include = TRUE, echo=TRUE}
day_and_hour <- data_2014 %>%
         group_by(day, hour) %>%
            dplyr::summarize(Total = n())

datatable(day_and_hour)

ggplot(day_and_hour, aes(day, hour, fill = Total)) +
            geom_tile(color = "white") +
              ggtitle("Heat Map by Hour and Day")

ggplot(day_month_group, aes(day, month, fill = Total)) +
            geom_tile(color = "white") +
              ggtitle("Heat Map by Month and Day")

ggplot(month_weekday, aes(dayofweek, month, fill = Total)) +
            geom_tile(color = "white") +
              ggtitle("Heat Map by Month and Day of Week")

month_base <-  data_2014 %>%
                    group_by(Base, month) %>%
                        dplyr::summarize(Total = n()) 

day0fweek_bases <-  data_2014 %>%
                    group_by(Base, dayofweek) %>%
                        dplyr::summarize(Total = n()) 

ggplot(month_base, aes(Base, month, fill = Total)) +
            geom_tile(color = "white") +
              ggtitle("Heat Map by Month and Bases")

ggplot(day0fweek_bases, aes(Base, dayofweek, fill = Total)) +
            geom_tile(color = "white") +
              ggtitle("Heat Map by Bases and Day of Week")
```

## Creating a map visualization of rides in New York


```{r include = TRUE, echo=TRUE}
min_lat <- 40.5774
max_lat <- 40.9176
min_long <- -74.15
max_long <- -73.7004

ggplot(data_2014, aes(x=Lon, y=Lat)) +
  geom_point(size=1, color = "blue") +
     scale_x_continuous(limits=c(min_long, max_long)) +
      scale_y_continuous(limits=c(min_lat, max_lat)) +
        theme_map() +
           ggtitle("NYC MAP BASED ON UBER RIDES DURING 2014 (APR-SEP)")

ggplot(data_2014, aes(x=Lon, y=Lat, color = Base)) +
  geom_point(size=1) +
     scale_x_continuous(limits=c(min_long, max_long)) +
      scale_y_continuous(limits=c(min_lat, max_lat)) +
       theme_map() +
          ggtitle("NYC MAP BASED ON UBER RIDES DURING 2014 (APR-SEP) by BASE")

```
